---
title: "Aides Drug"
author: "Brianna Olvera!"
date: "10/30/2019"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
avast <-read.csv(file="avastivironal.csv",header=TRUE)
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. Finish this!

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->

In this survery our two variables will be categorical vs categorical resulting in us using a barchart for our graphical method, a cross tabulation for our numerical results and taking a chisqtest for our inferential results. All questions and variables will be tested using this same method over the five questions throughout this survey being asked about the following: Total Population,Females,Males,DrugUsers, and LGBTQ.

## Q1: Does the vaccine have results on the Total Population for the survey?

$H_0$: The vaccine has no effect on whether one contracts aids or not.

$H_A$: The vaccine affects whether one contracts aids or not.

## Q2: Does the vaccine have results on just Females in the survey?

$H_0$: The vaccine has no effect on whether females contract aids or not

$H_A$: The vaccine affects whether females contract aids or not.

## Q3: Does the vaccine have results on just Males in the survey?

$H_0$: The vaccine has no effect on whether males contract aids or not.

$H_A$: The vaccine affects whether males contract aids or not.

## Q4: Does the vaccine have results on Drug Users in the survey?

$H_0$: The vaccine has no effect on whether drug users contract aids or not.

$H_A$: The vaccine affects whether drug users contract aids or not.

## Q5: Does the vaccine have results on the LGBTQ in this survey?

$H_0$: The vaccine has no effect on whether drug users contract aids or not.

$H_A$: The vaccine affects whether drug users contract aids or not.

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results


### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->

## Question1: Total Population

```{r}
barchartGC(~infected+treatment, type = "percent",main = "Total Population", horizontal = TRUE, data = filter(avast))
```

The barchart shows significant difference in the general population that took the drug verses the general population that took the placebo. When looking at the total population within the survey there is a clear difference in percentages amongst the aids group that was affected by the vaccine to the placebo group.

## Question2: Females

```{r}
barchartGC(~infected+treatment, type = "percent", main = "Females only", horizontal = TRUE, data = filter(avast, sex== "gal"))
```

The bar chart shows the effectiveness is related to gender, women are more susceptibleThe female only population in the survey appears to show a large difference within the percentages of the aids affected group. 

## Question3: Males
```{r}
barchartGC(~infected+treatment, type = "percent", main = "Males Only", horizontal = TRUE, data = filter(avast, sex=="guy"))
```

The barchart shows significant difference in the males that took the drug verses the males that took the placebo.  
The male population appears to show that the aids group given the drug has a higher percentage than the placebo group in the aids affected group.

## Question4: DrugUsers
```{r}
barchartGC(~infected+treatment, type = "percent", main = "DrugUsers", horizontal = TRUE, data = filter(avast, DrugUser=="yes"))
```

The barchart shows significant difference in the drug users that took the drug verses the drug users that took the placebo.The population of Drug Users within the survey shows that amongst the aids group those who were given the vaccine show a much lower percentage of being affected by aids than those in the same aids group who were given the placebo. 

## Question5: LGBTQ
```{r}
barchartGC(~infected+treatment, type = "percent", main = "LGBTQ", horizontal = TRUE, data= filter(avast,LGBTQ=="gay"))
```

The barchart shows significant difference in the LGBTQ that took the drug verses the LGBTQ that took the placebo. 
The population for LGBTQ within the survey show a large percentage of those still affected by aids even when taking the drug. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

## Question1: Total Population
```{r}
tab1 = xtabs(~infected+treatment, data = filter(avast))
rowPerc(tab1)
```

the Numerical results show that within the none group for the total population of those not affected by aids, show that there is no difference between taking the actual drug or placebo.

## Question2: Females
```{r}
tab2 = xtabs(~infected+treatment, data = filter(avast,sex=="gal"))
rowPerc(tab2)
```

The female only population appears to show that the drug cut the percentage of those affected by aids in half.


## Question3: Males
```{r}
tab3 = xtabs(~infected+treatment, data = filter(avast,sex=="guy"))
rowPerc(tab3)
```

The male only population appears to show a significant difference. That the drug seems to have some affect on contracting aids in the drug group.

## Question4: DrugUsers
```{r}
tab4 = xtabs(~infected+treatment, data = filter(avast,DrugUser=="yes"))
rowPerc(tab4)
```

The population of Drug Users appears to show that the group who were given the drug treatment amongst the aids group are at 1/4 of a difference from the total of aids infected from the placebo group.


## Question5: LGBTQ
```{r}
tab5 = xtabs(~infected+treatment, data = filter(avast,LGBTQ=="gay"))
rowPerc(tab5)
```

The population of LGBTQ appears to show that the drug group has a larger affected rate than that of the placebo group.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

## Question1: Total Population
```{r}
chisqtestGC(tab1)
```

For our total population we end up with a P-value of 0 < 0.05 so we reject the null hypothesis 

## Question2: Females
```{r}
chisqtestGC(tab2)
```

For our female only group we end up with a P-value of 0 < 0.05 so we reject the null hypothesis

## Question3: Males
```{r}
chisqtestGC(tab3)
```

For our male only group we end up with a P-value of 0.0004 < 0.05 so we reject the null hypothesis

## Question4: DrugUsers
```{r}
chisqtestGC(tab4)
```

For our population of Drug Users in the survey, there ends up being a P-value of 0 < 0.05 so we reject the null hypothesis 

## Question5: LGBTQ
```{r}
chisqtestGC(tab5)
```

For our population of LGBTQ in the survey we end up with a P-value of 0 < 0.05 so we reject the null hypothesis

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

Within the survey it appears that the drug has different effects amongst the groups in our survey, however the drug does show that it does affect every group within the survey. Amongst our total population, females and drug users it appears that the drug does help prevent these populations from contracting aids. But also appears that the drug makes males and LGBTQ more likely to contract aids if they are given the drug. This relationship of showing a higher rate of contracting aids amongst males and LGBTQ suprisingly still does not outweigh the prevention amongst the total population and females who are also involved within the drug users population. Throug the total data shown it can be the reason that for the most part the drug does help treat those infected with aids.


